SSA based global code motion of identical computations

### 2017-04-14 hoist.tex
cleanup from the write

The code-hoisting pass can be divided into the following steps that we will
describe in the rest of this section:
\begin{itemize}
\item find candidates: instructions computing same values,
\item compute a point in the program where it is both legal and profitable to
  move the code,
\item transform the code.
\end{itemize}

@@

\subsection{Code generation}
Once all the legality and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed, and the \SSA{} form is restored by updating the
intermediate representation (IR) to reflect the changes.

@@

Finally after the transform is done, we verify a set of post-conditions to
establish that program invariants are maintained: e.g., consistency of
use-defs, and \SSA{} semantics.

>>>>

The code-motion pass can be broadly divided into the following steps that we will
describe in the rest of this section:
\begin{itemize}
\item find candidates suitable for code-motion
\item compute a point in the program where it is both legal and profitable to
  move the code,
\item transform the code and update data structures to continue iterative code
  motion.
\end{itemize}

@@

\subsection{Code generation}
Once all the legality and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed, and the \SSA{} form is restored by updating the
intermediate representation (IR) to reflect the changes. At the same time
MemorySSA is also updated to get up-to-date information about memory references.

@@

Finally after the transformation is done, we verify a set of post-conditions to
establish that program invariants are maintained: e.g., consistency of use-defs,
and \SSA{} semantics.
